Variants on the Flight and Maintenance Planning problem

### 2018-06-22 latex/notes/complexite/FMP_variants.tex
new documents and presnetations or re-organised documents

% \bibliographystyle{dcu}
\bibliographystyle{alpha}
\bibliography{./../biblio/Scheduling,./../biblio/NRP}

>>>>

\section{Three partition problem}

    \begin{itemize}
     \item assigned maintenances at regular intervals of M.
     \item We need to assign tasks in between maintenances.
     \item Each task assignment needs M/3 consecutif periods.
     \item Each task assignment has an flight hours consumption.
    \end{itemize}

    \begin{itemize}
        \item Missions have a fixed duration.
        \item Maintenances are evenly spaced.
        %\item The missions require 0 aircraft at each period.
        % \item Each aircraft can only be used for one mission.
    \end{itemize}

    % \subsection{Limitations}

    % \begin{itemize}
    %     \item Resource usage is always 1.
    %     %\item There is only one type of resource.
    %     \item All durations are the same.
    % \end{itemize}

    \noindent{
    \begin{tabular}{ll}
        $i \in \II = [\![1, I]\!]$ & Set of aircraft.\\
        $k \in \KK_i = [\![1, K_i]\!]$ & Set of maintenances for aircraft $i$.\\ 
        $j \in J$ & Set of missions.\\ 
        % $i \in \mathcal{V} = [\![1, n]\!]$ & Set of maintenance operations.\\
        % $k \in \mathcal{R}$ & Types of resources that maintenance can take. We only have one type.\\
        % $i = 0$ & Artificial starting node.\\
        % $i = n+1$ & Artificial ending node.\\
    \end{tabular}
    }

    This doesn't make sense because the tasks are already defined. We cannot chose when it executes.

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \bibliographystyle{dcu}
\bibliographystyle{alpha}
\bibliography{./../biblio/Scheduling,./../biblio/NRP}
